Compositional equivalences based on Open pNets

### 2020-03-27 2016-Weak-FH-Bisim/WeakBisim.tex
developped example in page 26
check, acorrected, and completed use-case in page 26

  $ SS_3 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
  {b0 \OTWeakarrow {\underline{\texttt{in(m1)}}} b1}
  $

@@

$\forall m1. \{True \land True\hspace{3mm} \implies
\exists m2. \\
(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
\land True
\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}\\
\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
\subst{(\texttt{b1\_msg}\gets \texttt{m}, \texttt{b1\_ec}\gets 0)
  \uplus (\texttt{s1\_msg}\gets \texttt{m}, \texttt{s1\_ec}\gets 0)})\}
$

@@

  $ SI_{4} = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})}
         {100 \OTWeakarrow {\tau} 210}
         $

  $ WS_4(n) = \openrule
         {\{\}, True, (b1\_ec\gets b1\_ec+n)}
         {b1 \OTWeakarrow {\tau} b1}
         \ \forall n\ge 0
         $

  \medskip       A similar reasonning gives us\TODO{refaire}

         $\{b1_msg = s1_msg \land b1_ec = s1_ec \land True\hspace{3mm} \implies
\\
(\texttt{q-recv(s1-msg,s1-ec+n)} = \texttt{q-recv(msg,ec+n)}
\land True\\
\land \underline{\texttt{out(s1-msg,s1-ec+n)}} = {\underline{\texttt{out(msg,ec)}\subst{ec\gets ec+n}}}\\
\land True \subst{ec\gets ec+n})\}
$

>>>>

  $ SS_3 = \openrule
  {\{\texttt{P}\mapsto \texttt{p-send(m1)}\}, True,
    (\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)}
  {b0 \OTarrow {\underline{\texttt{in(m1)}}} b1}
  $

@@

$\forall m1. \{True \land True\hspace{3mm} \implies
\exists m2. \\
(\texttt{[p-send(m1)]} = \texttt{[p-send(m2)]}
\land True
\land \underline{\texttt{in(m1)}} = \underline{\texttt{in(m2)}}\\
\land (\texttt{b1\_msg = s1\_msg} \land \texttt{b1\_ec = s1\_ec})
\subst{(\texttt{b1\_msg}\gets \texttt{m1}, \texttt{b1\_ec}\gets 0)
  \uplus (\texttt{s1\_msg}\gets \texttt{m2}, \texttt{s1\_ec}\gets 0)})\}
$

@@

  $ SI_{4} = \openrule
         {\{\}, True, (\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec})}
         {100 \OTarrow {\tau} 210}
         $

  $ WS_4(n) = \openrule
         {\{\}, True, (\texttt{b1\_ec}\gets \texttt{b1\_ec}+n)}
         {b1 \OTWeakarrow {\tau} b1}
         \ \forall n\ge 0
         $

  \medskip       A similar reasonning gives us\TODO{Refait, please check. But I think it does not show much more than first case, can we find a better case ?}

\begin{itemize}
  \item No active holes and the pair of ressulting states $<210,b1>$ is in $\mathcal{R}$.
\item $fv(SI_4) = \{\}, fv(WS_4(n)) = \{n\}$, \TODO{Is that correct ? Is it true that considering $n$ as a free variable allows Z3 to find  a suitable value...?}
\item and the verification condition\\

         $(b1_msg = s1_msg \land b1_ec = s1_ec) \land True\hspace{3mm} \implies\\
\exists n.
( True \land \tau=\tau
\land (b1_msg = m1_msg \land b1_ec = m1_ec)  \subst{\texttt{m1\_msg}\gets \texttt{s1\_msg}, \texttt{m1\_ec}\gets \texttt{s1\_ec}, \texttt{s2\_ec}\gets \texttt{s1\_ec}}
\uplus \subst{\texttt{b1\_ec}\gets \texttt{b1\_ec}+n})
$

is easily proved True for $n=0$.
 \end{itemize}
